My title

### 2022-02-02 outputs/paper/paper.Rmd
upload

data_extract <-
  cleaned_data %>% 
    slice(1:10) %>%
      kable(
      caption = "First ten rows of a dataset of fire incidents in Toronto",
      col.names = c("Area of Origin", "Fire Alarm System Operation", "Extent of Fire", "Building Status", "Latitude", "Longitude", "Estimated Dollar Loss"),
      digits = 1,
      booktabs = TRUE, 
      linesep = ""
    ) %>%
  kable_styling(font_size = 4)

@@

graph_data %>% 
  select(fire_alarm_system_operation) %>%
  datasummary_skim(type = "categorical")
```

@@

outliers_sum <-
  outliers %>% 
    slice(1:4) %>%
      kable(
      caption = "Fire Incidents with Estimated Dollar Loss Exceeding $250,000",
      col.names = c("Fire Alarm System Operation", "# of Fire Incidents"),
      digits = 1,
      booktabs = TRUE, 
      linesep = ""
    )

outliers_sum
```

The outlier summary table shows the number of fire incidents with estimated dollar losses exceeding \$250,000, which are excluded from the histograms. As one may observe, the number of outliers with operating fire alarm systems is much lower than the rest of the three categories.

@@

final_map
```

# Results

>>>>

data_extract <-
  cleaned_data %>% 
    slice(1:10) %>%
      kable(
      caption = "First ten rows of a dataset of fire incidents in Toronto",
      col.names = c("Area of Origin", "Fire Alarm System Operation", "Extent of Fire", "Building Status", "Latitude", "Longitude", "Estimated Dollar Loss"),
      digits = 1,
      booktabs = TRUE, 
      linesep = ""
    ) %>%
  kable_styling(font_size = 4, latex_options = "HOLD_position")

@@

graph_data %>% 
  select(fire_alarm_system_operation) %>%
  datasummary_skim(type = "categorical") %>%
  kable_styling(latex_options = "HOLD_position")
```

@@

outlier_table <-
  outliers %>% 
    slice(1:4) %>%
      kable(
      caption = "Fire Incidents with Estimated Dollar Loss Exceeding $250,000",
      col.names = c("Fire Alarm System Operation", "# of Fire Incidents"),
      digits = 1,
      booktabs = TRUE, 
      linesep = ""
    ) %>%
  kable_styling(latex_options = "HOLD_position")

outlier_table
```

@@

final_map
```
# Results
